Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-02-28 Paper.tex
EIP86: preparation before adding CREATE_P2SH
The function \Lambda now takes the new address as a parameter

where $g$ is the amount of gas remaining after deducting the basic amount required to pay for the existence of the transaction:
\begin{equation}
g \equiv T_g - g_0
\end{equation}
and $T_o$ is the original transactor, which can differ from the sender in the case of a message call or contract creation not directly triggered by a transaction but coming from the execution of EVM-code.  $a$ is the address of the created account:
\begin{equation} \label{eq:address_calc}
a \equiv \mathcal{B}_{96..255}\Big(\mathtt{\tiny KEC}\big(0 \cdot \mathbf{i}\big)\Big)
\end{equation}
where $0$ denotes the zero element of $\mathbb{B}_{160}$, the operator $\cdot$ is the concatenation of binary data, $\mathtt{\tiny KEC}$ is the Keccak 256-bit hash function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data.

@@

When a transaction has a particular invalid signature $v = r = s = 0$, the sender of the transaction is $2^{256} - 1$.
\begin{equation}
\forall T: S(T) \equiv 2^{256} - 1 \quad \text{ where } (T_w, T_r, T_s) = (0, 0, 0).
\end{equation}

>>>>

where $g$ is the amount of gas remaining after deducting the basic amount required to pay for the existence of the transaction:
\begin{equation}
g \equiv T_g - g_0
\end{equation}
and $T_o$ is the original transactor, which can differ from the sender in the case of a message call or contract creation not directly triggered by a transaction but coming from the execution of EVM-code.  $a$ is the address of the created account, which is defined as the rightmost 160 bits of the Keccak hash of the RLP encoding of the structure containing only the sender and the nonce. Thus we define the resultant address for the new account $a$:
\begin{equation}
a \equiv \mathcal{B}_{96..255}\Big(\mathtt{\tiny KEC}\Big(\mathtt{\tiny RLP}\big(\;(s, \boldsymbol{\sigma}_0[s]_n - 1)\;\big)\Big)\Big)
\end{equation}

where $\mathtt{\tiny KEC}$ is the Keccak 256-bit hash function, $\mathtt{\tiny RLP}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$ and $\boldsymbol{\sigma}_0[x]$ is the account state of $x$ or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

@@

When a transaction has a particular invalid signature and it has zero gas price, zero nonce and zero value, the sender of the transaction is $2^{256} - 1$.
\begin{equation}
\forall T: S(T) \equiv 2^{256} - 1 \quad \text{ where } \quad (T_w, T_r, T_s) = (\mathtt{chain\_id}, 0, 0) \,\wedge\, T_p = T_n = T_v = 0.
\end{equation}
